Presheaf Model for Dependent Types

### 2017-09-21 papers/talk-11/paper-11.tex

@@

In the following, we will omit the indices on $\sigma$; Then if we write
$\Gamma_f$ and $\Delta_f$ as $f$ acting on the right, the equation becomes:
\[
  (\sigma \rho) f = \sigma (\rho f)
\]
for $\rho$ in $\Delta(I)$.

@@

\begin{example}[Ordinary function type]
  Let us consider a term of type $A \to A$, and the elements in $Ty(\Gamma)$
  and $Ter(\Gamma, A \to A)$ for some $\vdash \Gamma~ctxt$, $\Gamma \vdash
  A~type$.

@@

\section*{Conclusion}

>>>>

\bibliographystyle{plainurl}

@@

In the following, we will omit the indices on $\sigma$; Then if we write
$\Gamma_f$ and $\Delta_f$ as $f$ acting on the right (recall the session on
presheaves), the equation becomes:
\[
  (\sigma \rho) f = \sigma (\rho f)
\]
for $\rho$ in $\Delta(I)$.

@@

\begin{example}
  Let us consider a term of type $A \to A$, and the elements in $Ty(\Gamma)$
  and $Ter(\Gamma, A \to A)$ for some $\vdash \Gamma~ctxt$, $\Gamma \vdash
  A~type$ in the presheaf model.

@@

\section*{Credits}

Most of the material on the dependent types bases on \cite{Hofmann}, while
starting from categories with families we closely follow \cite{Huber}.

\bibliography{main}
